---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saens

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/saens)](https://CRAN.R-project.org/package=saens) [![R-CMD-check](https://github.com/Alfrzlp/saens/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Alfrzlp/saens/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

## Author

Ridson Al Farizal P, Azka Ubaidillah

## Maintainer

Ridson Al Farizal P [alfrzlp\@gmail.com](mailto:alfrzlp@gmail.com){.email}

## Description

The goal of saens is to ...

## Installation

You can install the development version of saens from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("Alfrzlp/saens")
```

or you can install cran version

```{r, eval=FALSE}
install.packages(saens)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(saens)
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r cars}
glimpse(mys)
```

### EBLUP Model

```{r}
m1 <- eblupfh(y ~ x1 + x2 + x3, data = mys, vardir = "var", cluster = "clust")
```

### Comparison of estimates and RSE

```{r}
mys$eblup_est <- m1$df_res$eblup
mys$eblup_rse <- m1$df_res$rse
  
glimpse(mys)
```

```{r}
mys %>% 
  select(area, rse, eblup_rse) %>% 
  pivot_longer(-1, names_to = "metode", values_to = "rse") %>%
  ggplot(aes(x = area, y = rse, col = metode)) +
  geom_line() +
    scale_color_discrete(
    labels = c('EBLUP', 'Direct Estimate')
  ) +
  labs(col = NULL, y = 'Estimate', x = 'Domain', title = 'Comparison of RSE') +
  theme(
    legend.position = 'bottom',
    text = element_text(family = 'poppins'),
    axis.ticks.x = element_blank(),
    plot.title = element_text(face = 2, vjust = 0),
    plot.subtitle = element_text(colour = 'gray30', vjust = 0)
  )
```

```{r}
mys %>% 
  select(area, y, eblup_est) %>% 
  pivot_longer(-1, names_to = "metode", values_to = "rse") %>%
  ggplot(aes(x = area, y = rse, col = metode)) +
  geom_line() +
    scale_color_discrete(
    labels = c('EBLUP', 'Direct Estimate')
  ) +
  labs(col = NULL, y = 'Estimate', x = 'Domain', title = 'Comparison of Estimates') +
  theme(
    legend.position = 'bottom',
    text = element_text(family = 'poppins'),
    axis.ticks.x = element_blank(),
    plot.title = element_text(face = 2, vjust = 0),
    plot.subtitle = element_text(colour = 'gray30', vjust = 0)
  )
```
